\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} \hfill \textbf{#2}\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} #2 $\bullet$ #3\\
#4 $\bullet$  Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1}, #2 \hfill \textbf{#3}\\
 \textsl{#4} \\
}
\newcommand{\schooll}[5]{
 \textbf{#1}, #2 \hfill \textbf{#3}\\
 \textsl{#4}\\
 \textsl{#5} \\
}
\newcommand{\english}[2]{
 {#1} \hfill {#2}
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}
%----------------------------------contact------------------------------------------
\contact{Zhensong Zhang}
{RM 701, BULD 5, 4\# South Fourth Street, Zhongguancun, Beijing, P. R. China, 100190}
{mobile: (86) 18810460107 $\bullet$ email: zhensongzhang@gmail.com}
%----------------------------------contact------------------------------------------

%----------------------------------education----------------------------------------
\header{Education}

\schooll{University of Chinese Academy of Sciences}{\textsl{Beijing}, P.R. China}{ Sep. 2011 -- Present}
{(Institute of Software Chinese Academy of Sciences)}
{Master of Science, Computer Applied Technology}
\vspace{2mm}
\school{Xidian University}{\textsl{Xi'an}, P.R. China}{ Sep. 2007 -- Jul. 2011}{Bachelor of Engineering, Software Engineering}
Dissertation: Merging Domain-Specific Web Search Interfaces of the Deep Web \\
\vspace{2mm}
%----------------------------------education----------------------------------------

%----------------------------------publications-------------------------------------
\header{Publications}
\begin{achievements}
\item \textbf{Zhang, Z.}, et al. Hierarchical Cursor: Pointing on Large Displays using Smartphones. In preparation.
\item \textbf{Zhang, Z.}, Zhang, F., Chen, H., Liu, J., Wang, H. and Dai, G. Left and Right Hand Distinction for Multi-Touch Tabletop Interactions. \textsl{Proc. IUI 2014}, Pages 47-56.
\item Liu, J., Zhang, F., \textbf{Zhang, Z.}, Chen, H., Dai, G., and Wang, H. Left-Right Hand Distinction System for Multi-Touch Tabletop. \textsl{Journal of Software}, 2014, 25(5), Pages 939-952.
\item Li, Y., Wang, Y., Jiang, P., \textbf{Zhang, Z.} Multi-objective optimization integration of query interfaces for the Deep Web based on attribute constraints. \textsl{Data \& Knowledge Engineering}, Volume 86, July 2013, Pages 38-60.
\item Li, Y., Wang, Y., Yang, X., \textbf{Zhang, Z.}, Zheng, Y., and Zheng, L. NMLCS: A Novel Parallel Algorithm for Searching for the Multiple Longest Common Subsequences. \textsl{Energy Procedia}, Volume 11, 2011, Pages 1392-1404.
\end{achievements}
%----------------------------------publications-------------------------------------

%----------------------------------research projects--------------------------------
\header{Selected Professional Experience}
\employer{Markerless Real Time Camera Tracking System}{Dec. 2012 - Present}{Designer and Developer}
	\begin{achievements}
	\item Dissertation research on implementing a SLAM/PTAM system.
	\item Using camera images only to estimate the pose and position of a moving camera in an unknown environment in real time.
	\end{achievements}

\employer{Large Display Based Interactive System}{May 2013 - Aug. 2013}{Main Developer}
	\begin{achievements}
	\item Collecting sensor information from smart devices (phones/pads), and estimating the devices¡¯ poses to interact with a large display.
    \item Users can view the 3D world in 3 modes (driving, track ball, flight) , pick and modify (scale/rotate/translate) objects.
    \item Several users can simultaneously interact with different objects on the same large display.
	\end{achievements}

\employer{Left and Right Hand Distinction System for Multi-Touch Tabletop}{Oct. 2012 - Nov. 2012} {Designer and Developer}
	\begin{achievements}
	\item Analyzing the interactive video using OpenCV and figuring out the relationships between the fingers.
	\item Proposed a heuristic method to distinguish left hand from right hand.
	\end{achievements}

%----------------------------------research projects--------------------------------

%-------------------------------------Honors and Awards----------------------------------------
\header{Honors and Awards}
\begin{achievements}
\item \textbf{SIGAI IUI 2014 Travel Grants}, ACM \hfill \textbf{2014}
\item \textbf{National Scholarship}, University of Chinese Academy of Sciences \hfill \textbf{2\%, 2013}
\item \textbf{Merit Student}, University of Chinese Academy of Sciences \hfill \textbf{15\%, 2012 \& 2013}
\item Privilege to enter the Graduate Program of Institute of Software Chinese
Academy of Sciences, waived of Entrance Test \hfill \textbf{2011}
\item \textbf{Excellent Student Cadre}, Xidian University \hfill \textbf{1\%, 2009 \& 2011}
\item \textbf{Merit Student}, Xidian University \hfill \textbf{3\%, 2008 \& 2010}
\item \textbf{The First Class Scholarship for Academic Achivement}, Xidian University \hfill \textbf{3\%, 2008 \& 2010}
\item \textbf{National Scholarship for Encouragement}, Xidian University \hfill \textbf{3\%, 2009}

\end{achievements}
%-------------------------------------Honors and Awards----------------------------------------

%-------------------------------------Extracurricular Activities---------------------------
\header{Extracurricular Activities}
\begin{achievements}
\item Member of Open Source Club of University of Chinese Academy of Sciences \hfill \textbf{2011 - Present}
\item The network administrator of Intelligence Engineering Lab, Institute of Software, Chinese Academy of Sciences  \hfill \textbf{2012 - 2013}
\item The Minister of Propaganda Department of the Student Union of the Department of Computer
and Information Science and Engineering, University of Chinese Academy of Sciences \hfill \textbf{2011 - 2012}
\item The Minister of Propaganda Department of the Student Union of the Department of Freshmen, Xidian University \hfill \textbf{2007 - 2008}

\end{achievements}
%-------------------------------------Extracurricular Activities----------------------------

%-------------------------------------Skills----------------------------------------
\header{Computer Skills and Other Proficiencies}
\begin{achievements}
\item Programming: C/C++, Java, Matlab, Python, SQL.
\item Libraries: OpenCV, OpenSceneGraph, OpenGL, boost.
\item Platform: Windows 7/XP, LINUX, Android.
\item Others: Network Programming, Parallel programming, \LaTeX.
\end{achievements}

%-------------------------------------Skills----------------------------------------


\end{document}
